\subsection{REST Error Codes}

Here the list of errors defined in the application. Application specific errors have the application error which follows a progressive numeration starting from -100. METHOD NOT ALLOWED errors are identified with the error code -500. Internal errors, which correspond to crashes, servlet exceptions, or problems with the input/output streams are identified with the Error Code -999.

\begin{longtable}{|p{.15\columnwidth}|p{.3\columnwidth} |p{.5\columnwidth}|} 
\hline
\textbf{Error Code} & \textbf{HTTP Status Code} & \textbf{Description} \\\hline
-  0  & OK                       & Indicates that the request has succeeded. \\ \hline
-100  & NOT\_FOUND               & User not found\\ \hline
-101  & CONFLICT                 & User already exists.. \\ \hline
-102  & Unauthorized             & User not authorized. \\ \hline
-103  & NOT\_FOUND               & Template not found.\\ \hline
-104  & BAD\_REQUEST             & Template information missing upon making a request. \\ \hline
-105  & CONFLICT                 & Template already exists.. \\ \hline
-106  & NOT\_FOUND               & Analytics not found.\\ \hline
-107  & NOT\_FOUND               & Workspace not found.\\ \hline
-108  & NOT\_FOUND               & Assignee not found.\\ \hline
-109  & NOT\_FOUND               & Comment not found.\\ \hline
-110  & NOT\_FOUND               & Activity not found.\\ \hline
-111  & NOT\_FOUND               & Board not found.\\ \hline
-112  & NOT\_FOUND               & SubBoard not found.\\ \hline
-200  & Created                  & Indicates that the request has succeeded and a new template has been created as a result. \\ \hline
-201  & Created                  & Indicates that the request has succeeded and a new user has been created as a result. \\ \hline
-202  & Created                  & Indicates that the request has succeeded and a new workspace has been created as a result. \\ \hline
-203  & Created                  & Indicates that the request has succeeded and a board has been created as a result. \\ \hline
-204  & Created                  & Indicates that the request has succeeded and a comment has been created as a result. \\ \hline
-999  & Internal\_Server\_Error  & The server encountered an unexpected condition that prevented it from fulfilling the request. \\ \hline
-1000 & METHOD\_NOT\_ALLOWED     & Method not allowed. \\ \hline
-1002 & BAD\_REQUEST             & Wrong REST format. \\ \hline
-1004 & BAD\_REQUEST             & Operation unknown. \\ \hline

\caption{Error codes for the REST interface of the Amusement Park application back-end}
\label{tab:termGlossary}
\end{longtable}